Appendix

### 2021-05-11 paper/preprint/paper_revised_submission_april2021_apa.Rmd
discussion minor edits

# Results and Discussion

## Access to social information across age
```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_joint_given_faces = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_joint_given_hands = sum(faces_and_hands, na.rm=TRUE)/num_hands,
            prop_joint_given_faces_center = sum(face_and_hands_center, na.rm=TRUE)/num_faces_center, 
            prop_joint_given_hands_center = sum(face_and_hands_center, na.rm=TRUE)/num_hands_center)

@@

<!-- FIXME - references not rendering for -->
As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%. This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:FacesAndHands}). We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure\ref{fig:goldSetSanity}).

@@

How does the child's context influence the social information in view? 
@bruner1985role discussed the role of children's activities in shaping the information present for learning. Following this idea, we investigated whether there were differences in access to faces by the activity that the child was engaged in. 
This hypothesis seems intuitively appealing.  
Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). 
Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime).

We did not have access to annotations of activity. 
Thus, following @roy2015predicting, we used spatial location as a proxy for activity context, taking advantage of the presence of these annotations for a subset of the SAYCam videos. 
Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
These location annotations were only available for two children, S and A.
Annotated locations mostly consisted of rooms of the house (e.g., "living room") but also included some other locations (e.g., "car," "outside").
Of this set, `r videos_included` videos were filmed in only a single location (e.g., the location label did not change within the video), representing 17 percent of the dataset and over 5 million frames. 
In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.

Figure \ref{fig:DetByLocation} shows the proportion of faces vs. hands across locations. 
We found substantial variation across locations and, to some extent, across children. 
Separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case, with all $p$s $<.001$. 
For example, while both A and S saw a relatively similar proportion of faces and hands in the bedroom, the two children saw quite different amounts of faces and hands from one another in the kitchen. 
This difference is likely explained by differences in arrangement of the kitchen in the two children's households (Sullivan, personal communication), such that mealtimes in one kitchen resulted in a face-to-face orientation while it did not in the other). 
This example illustrates how specifics of the geometry of a particular context can play an outsize role in the child's access to social information during that context.

## Fine-grained changes in the social information in view

```{r}
## construct age bins for plotting
bin_size=7
min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

@@

# General Discussion

Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age. First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016]. This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].  We also found this to be true when restricting our analyses to full-field faces, suggesting this effect is not driven by a concurrent shift from more full-view to partial-views of faces.

@@

We also found changes in how children experienced faces and hands over development: we found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions.  Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile an independent. As children can navigate the world on their own, they may experience fewer close-up interactions with the caregivers and more bouts of play where they are exploring the objects and things in the environment around them.

>>>>

# Results
## Access to social information across age
```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_joint_given_faces = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_joint_given_hands = sum(faces_and_hands, na.rm=TRUE)/num_hands,
            prop_joint_given_faces_center = sum(face_and_hands_center, na.rm=TRUE)/num_faces_center, 
            prop_joint_given_hands_center = sum(face_and_hands_center, na.rm=TRUE)/num_hands_center)

@@

As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%. This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:FacesAndHands}). We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure\ref{fig:goldSetSanity}).

@@

How does variability across different learning contexts influence the social information in the infant view? Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room). We thus next examined variation in presence of hands and faces across different locations. Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location they were filmed in. Of these, `r videos_included` videos were filmed in single location, representing 17 percent of the dataset and over 5 million frames. Activities varied somewhat predictably by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room. Overall, we found that the proportion of faces vs. hands varied across filming locations, and, to some extent, across children; separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case ^[all *p*<.001, see accompanying codebase]. For example, while both A and S saw a relatively similar proportion of faces vs. hands in the bedroom, they saw quite different amounts of faces vs. hands in kitchens (see Figure \ref{fig:DetByLocation}).

## Fine-grained changes in the social information in view
```{r}
## construct age bins for plotting
bin_size=7
min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

@@

# General Discussion
Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age. First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016]. This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].  We also found this to be true when restricting our analyses to full-field faces, suggesting this effect is not driven by a concurrent shift from more full-view to partial-views of faces.

@@

We also used these detailed pose annotations to explore finer-grained changes in how children experience the faces and hands of their caregivers over development. We found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions.  Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile an independent. As children can navigate the world on their own, they may experience fewer close-up interactions with the caregivers and more bouts of play where they are exploring the objects and things in the environment around them.
